Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-19 main.tex
sequentialization

@@

\begin{proof}
  Consider the frame $\lambda_m$ of $\lambda$. The number of any switching
graph of $\unifstr{\lambda}$ is equal to that of $\unifstr{\lambda_m}$. Apply
Lemma \ref{lem:concomp_switching} and it is clear that such $\vlor$ cannot be one
of the fresh $\vlor$'s added during the frame construction.
\todo{}
\end{proof}

\begin{proof}\label{lem:concomp_switching_fo}
Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
number of connected components of the unification structure $\unifstr{\lambda}$:
\begin{itemize}
  \item If there is only one connected component, we proceed by induction on the
number $k$ of connected components of any switching graph of
$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Pi$ in $\FOMLL$ such that
$\sqntl{\Pi} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
induction hypothesis, there is a proof $\Pi'$ in $\FOMLL$ whose translation is
$\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
node in $\Pi'$, we have:
$
\Pi' =
\vlderivation{
  \vlin{}{}{\sqns{\Gamma'}}{
  \vlin{}{}{\vlvdots}{
    \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
      \vltrl{\Pi_1}{}{}{\sqns{\Delta_1, A}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}{
      \vltrl{\Pi_2}{}{}{\sqns{B, \Delta_2}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}
}}}
$.
We can thus obtain a proof $\Pi$ of $\Gamma$:
$
\Pi =
\vlderivation{
  \vlin{}{}{\sqns{\Gamma}}{
  \vlin{}{}{\vlvdots}{
    \vlin{\vlor}{}{\sqns{\Delta_1, A \vlor B, \Delta_2}}{
    \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
      \vltrl{\Pi_1}{}{}{\sqns{\Delta_1, A}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}{
      \vltrl{\Pi_2}{}{}{\sqns{B, \Delta_2}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}
}}}}
$.

\todo{}
\end{itemize}

>>>>

\begin{proof}
Suppose that such $\vlor$ node does not exist.
\todo{}
\end{proof}

@@

\begin{proof}
  Consider the frame $\lambda_m$ of $\lambda$. The number of any switching
graph of $\unifstr{\lambda}$ is equal to that of $\unifstr{\lambda_m}$. Apply
Lemma \ref{lem:concomp_switching} and it is clear that such $\vlor$ cannot be one
of the fresh $\vlor$'s added during the frame construction.
\end{proof}

\begin{proof}\label{lem:concomp_switching_fo}
Let $\lambda$ be a unification net on $\Gamma$. We proceed by induction on the
number of connected components of the unification structure $\unifstr{\lambda}$:
\begin{itemize}
  \item If there is only one connected component, we proceed by induction on the
number $k$ of connected components of any switching graph of
$\unifstr{\lambda}$. If $k = 1$, we obtain a proof $\Deri$ in $\FOMLL$ such that
$\sqntl{\Deri} = \lambda$ by applying \cite[Theorem~3]{hughes:unifn}. If $k > 1$,
using the Lemma \ref{lem:concomp_switching_fo}, we obtain a sequent $\Gamma'$ on
which $\lambda$ is correct by transforming a $\vlor$ node into a $\vlan$. By
induction hypothesis, there is a proof $\Deri'$ in $\FOMLL$ whose translation is
$\lambda$. By considering the $\vlan$ rule instance corresponding to the $\vlan$
node in $\Deri'$, we have:
$
\Deri' =
\vlderivation{
  \vlin{}{}{\sqns{\Gamma'}}{
  \vlin{}{}{\vlvdots}{
    \vliin{\vlan}{}{\sqns{\Delta_1, A \vlan B, \Delta_2}}{
      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}{
      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}
}}}
$.
We can thus obtain a proof $\Deri$ of $\Gamma$:
$
\Deri =
\vlderivation{
  \vlin{}{}{\sqns{\Gamma}}{
  \vlin{}{}{\vlvdots}{
    \vlin{\vlor}{}{\sqns{\Delta_1, A \vlor B, \Delta_2}}{
    \vliin{\mix}{}{\sqns{\Delta_1, A, B, \Delta_2}}{
      \vltrl{\Deri_1}{}{}{\sqns{\Delta_1, A}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}{
      \vltrl{\Deri_2}{}{}{\sqns{B, \Delta_2}}{
        \vlhy{\quad}}{
        \vlhy{}}{
        \vlhy{}}}
}}}}
$ such that $\sqntl{\Deri} = \lambda$.

  \item If there are $n > 1$ connected components, add a fresh $\vlor$ node
connecting two formulas belonging to different connected components of $\Gamma$
to get a new sequent $\Gamma'$. Define a unification net $\lambda'$ on $\Gamma'$
using the same linking as $\lambda$. By induction hypothesis, since
$\unifstr{\lambda'}$
has $n-1$ connected components, there is a $\FOMLL$ proof $\Deri'$ such that
$\sqntl{\Deri'} = \lambda'$. Consider the $\vlor$ rule instance corresponding
to the $\vlor$ node in question. Since $\vlor$ is invertible, we can permute
downwards this rule instance until it becomes the last rule of the proof (note
that this transformation does not change the image of the proof by the
translation $\sqntl\cdot$) to get a new proof $\Deri''$ of $\Gamma'$. By deleting the last rule
instance from $\Deri''$, we obtain a proof $\Deri$ of $\Gamma$ such that
$\sqntl{\Deri} = \lambda$.
\tocheck{}
\end{itemize}
